TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-10 paper/draft.tex
restructure order of sections: (2) data, (3) methods, (4) sample selection
remove redundancies describing the cannon

% ----------------------------------------
\subsection{Training Sample Selection}

\thecannon\ is a pixel-by-pixel regression for spectral data given a training set of stars with reliable (assumed) accurate labels. The model can both predict a spectrum given labels, and also predict labels given a spectrum. Thus it is a generative model for stellar spectra that can be used for parameter inference.

>>>>

%%==========================================================================================
\section{Sample Selection}
